An Improved Approximate-Bayesian Model-choice Method for Estimating Shared Evolutionary History

### 2014-02-24 manuscripts/dpp-msbayes/dpp-msbayes-si-figures.tex
Working on dpp manuscript.
Proofreading and incorporating edits throughout the manuscript.
More editing of DPP ms.
Updating figures for dpp ms.
Using compressed and bitmapped versions of some of the more
vector-graphic-dense figures for the DPP ms.

%% Validation accuracy
\siFigure{../../validation/images/validation-accuracy-omega.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeDispersion}
}{figValidationAccuracyOmega}

\siFigure{../../validation/images/validation-accuracy-omega-glm.pdf}{
    \validationAccuracyComparisonCaption{GLM-adjusted}{\divTimeDispersion}
}{figValidationAccuracyOmegaGlm}

\siFigure{../../validation/images/validation-accuracy-time.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeMean}
}{figValidationAccuracyTime}

\siFigure{../../validation/images/validation-accuracy-time-glm.pdf}{
    \validationAccuracyComparisonCaption{GLM-adjusted}{\divTimeMean}
}{figValidationAccuracyTimeGlm}

\siFigure{../../validation/images/validation-accuracy-psi.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeNum}
    \jitterComment
}{figValidationAccuracyPsi}

\siFigure{../../validation/images/validation-accuracy-psi-glm.pdf}{
    \validationAccuracyComparisonCaption{GLM-adjusted}{\divTimeNum}
    \jitterComment
}{figValidationAccuracyPsiGlm}

@@

%% Validation ordered models
\siFigure{../../validation/no-sort/results/pymsbayes-results/plots/prior-dpp_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPPOrdered}{\modelDPPOrdered}
}{figValidationAccuracyDPPOrderedDPPOrdered}

@@

%% Power accuracy results
\siSidewaysFigure{../../power-comparison/images/old-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesOld}
}{figPowerAccuracyOld}

\siSidewaysFigure{../../power-comparison/images/uniform-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesUniform}
}{figPowerAccuracyUniform}

\siSidewaysFigure{../../power-comparison/images/exp-power-omega-accuracy-6.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesExp}
}{figPowerAccuracyExp}

@@

\siFigure{../../empirical-analyses/plots/negros-panay-marginal-times.pdf}{
    The marginal divergence-time results when the 9 pairs of taxa from the
    Islands of Negros and Panay are analyzed under the \npModelDPPOrdered model
    that samples over ordered models of divergence
    (Table~\ref{tabEmpiricalModels}).
}{figMarginalTimes}

>>>>

%% Validation accuracy
% \siFigure{../../validation/images/validation-accuracy-omega.pdf}{
\siFigure{../../validation/images/validation-accuracy-omega-compress.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeDispersion}
}{figValidationAccuracyOmega}

% \siFigure{../../validation/images/validation-accuracy-omega-glm.pdf}{
\siFigure{../../validation/images/validation-accuracy-omega-glm-compress.pdf}{
    \validationAccuracyComparisonCaption{GLM-adjusted}{\divTimeDispersion}
}{figValidationAccuracyOmegaGlm}

% \siFigure{../../validation/images/validation-accuracy-time.pdf}{
\siFigure{../../validation/images/validation-accuracy-time-compress.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeMean}
}{figValidationAccuracyTime}

% \siFigure{../../validation/images/validation-accuracy-time-glm.pdf}{
\siFigure{../../validation/images/validation-accuracy-time-glm-compress.pdf}{
    \validationAccuracyComparisonCaption{GLM-adjusted}{\divTimeMean}
}{figValidationAccuracyTimeGlm}

% \siFigure{../../validation/images/validation-accuracy-psi.pdf}{
\siFigure{../../validation/images/validation-accuracy-psi-compress.pdf}{
    \validationAccuracyComparisonCaption{unadjusted}{\divTimeNum}
    \jitterComment
}{figValidationAccuracyPsi}

% \siFigure{../../validation/images/validation-accuracy-psi-glm.pdf}{
\siFigure{../../validation/images/validation-accuracy-psi-glm-compress.pdf}{
    \validationAccuracyComparisonCaption{GLM-adjusted}{\divTimeNum}
    \jitterComment
}{figValidationAccuracyPsiGlm}

@@

%% Validation ordered models
% \siFigure{../../validation/no-sort/results/pymsbayes-results/plots/prior-dpp_prior-dpp_accuracy.pdf}{
\siFigure{../../validation/no-sort/results/pymsbayes-results/plots/prior-dpp_prior-dpp_accuracy-compress.pdf}{
    \validationAccuracyCaption{\modelDPPOrdered}{\modelDPPOrdered}
}{figValidationAccuracyDPPOrderedDPPOrdered}

@@

%% Power accuracy results
% \siSidewaysFigure{../../power-comparison/images/exp-power-omega-accuracy-6.pdf}{
\siSidewaysFigure{../../power-comparison/images/exp-power-omega-accuracy-6-compress.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesExp}
}{figPowerAccuracyExp}

% \siSidewaysFigure{../../power-comparison/images/uniform-power-omega-accuracy-6.pdf}{
\siSidewaysFigure{../../power-comparison/images/uniform-power-omega-accuracy-6-compress.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesUniform}
}{figPowerAccuracyUniform}

% \siSidewaysFigure{../../power-comparison/images/old-power-omega-accuracy-6.pdf}{
\siSidewaysFigure{../../power-comparison/images/old-power-omega-accuracy-6-compress.pdf}{
    \powerAccuracyComparisonCaption{\powerSeriesOld}
}{figPowerAccuracyOld}

@@

\siFigure{../../empirical-analyses/plots/negros-panay-marginal-times.pdf}{
    The marginal divergence-time results when the 9 pairs of taxa from the
    Islands of Negros and Panay are analyzed under the \npModelDPPOrdered model
    that samples over ordered models of divergence
    (Table~\ref{tabEmpiricalModels}).
    The times indicate the posterior median and 95\% highest posterior density
    (HPD) interval.
}{figMarginalTimes}
